(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-04 ms.tex
Some words on multis.

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci. 
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm 
\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
at the \btmtodo{confidence} level.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
orbital period of 33 days.
\anytodo{Anything we should add?}
\end{abstract}

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties. 
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}. 
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6 
\btmtodo{Cite: Who?}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties 
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the four WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit.
These data are reported in Table 1.

\btmtodo{Make this table!}

@@

We observed EPIC 201912552 on (all UT) February 04 2015, February 24 2015,
and February \btmtodo{XX} 2015 with the Tillinghast Reflector Echelle
Spectrograph (TRES) on the 1.5 m Tillinghast Reflector at the Fred L.
Whipple Observatory. 
These dates were chosen to be near the times of largest RV variations, 
corresponding to phases of \btmtodo{PHASES} relative to the time
of transit.
The spectra were taken with a resolving power of $R=44,000$ and 
integration times ranging from 2800 to 3600 seconds, resulting in 
signal-to-noise ratios between 17 and 29 per resolution element.

@@

The two observed spectra have RVs that differ by $47.1 \pm xx.x$ m s$^{-1}$.
A deviation at this magnitude can only be explained by the presence of 
a planetary system and instrumental noise, eliminating the possibility the
transiting planet is actually a false positive.

The observed radial velocities are included in Table \ref{Tab:RVs}.

\btmtodo{RVs table}

%57057.83314
%57077.75616

@@

This star is an M2.8 dwarf at a distance of \btmtodo{Distance: around 30 pc}.
Of our planet candidate hosts, only EPIC 201367065 \citep[originally
discovered by][]{Crossfield15} is brighter in $K$-band.
This star is only 0.1 magnitudes fainter in $K$ than GJ\,1214 
\citep{Charbonneau09}.
Due to the relative brightness of the host star, this target is likely
to become a prime target for atmospheric characterization studies
and is ideal as a target for future space-based missions such as JWST.

Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated. 
Instead, it is at an reduced semimajor axis \ars$ = 82.1 \pm 8.6$.
Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 275 \pm 15$
K, meaning its bulk insolation is similar to that of the Earth's.
Although the planet is likely too large to be rocky \citep{Rogers14}, 
its atmosphere is likely to be the focus of many future observations, providing
a cool analogue to the highly irradiated planets of a similar size found by 
\kep.

\subsection{EPIC 201465501?}
Is this a subsection? It's a star with a mass of ~0.2 Msun and a cnadidate with
a period of 18 days. I suppose it depends on the FPP.

@@

\subsection{Multiple Planet Systems}

@@

\acknowledgements
We thank [Eric Agol (UW) and Other People] for [things] which improved the quality of this manuscript.

>>>>

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci. 
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm 
\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
at the \btmtodo{confidence} level.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an 
orbital period of 33 days.
\anytodo{Anything we should add?}
\end{abstract}

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties. 
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}. 
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6 
\btmtodo{Cite: Who?}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties 
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the $W1-W3$ WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit,
and in the remaining two cases, the photometric uncertainity in $W4$ is at least an 
order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
These data are reported in Table 1.

@@

We observed EPIC 201912552 on (all UT) February 04 2015 and February 24 2015 
with the Tillinghast Reflector Echelle
Spectrograph (TRES) on the 1.5 m Tillinghast Reflector at the Fred L.
Whipple Observatory. 
These dates were chosen to be near the times of largest RV variations, 
corresponding to phases of 0.72 and 0.32 relative to the time
of transit.
The spectra were taken with a resolving power of $R=44,000$ and 
integration times ranging from 2800 to 3600 seconds, resulting in 
signal-to-noise ratios between 17 and 29 per resolution element.

@@

The two observed spectra have RVs that differ by $47.1 \pm 41.9$ m s$^{-1}$.
A deviation at this magnitude can only be explained by the presence of 
a planetary system and instrumental noise, eliminating the possibility the
transiting planet is actually a false positive.

@@

This star is an M2.8 dwarf at a distance of $34\pm4$ pc.
Of our planet candidate hosts, only EPIC 201367065 \citep[originally
discovered by][]{Crossfield15} is brighter in $K$-band.
This star is only 0.1 magnitudes fainter in $K$ than GJ\,1214 
\citep{Charbonneau09}.
Due to the relative brightness of the host star, this target is likely
to become a prime target for atmospheric characterization studies
and is ideal as a target for future space-based missions such as JWST.

Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated. 
Instead, it is at an reduced semimajor axis \ars$ = 82.1 \pm 8.6$.
Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 275 \pm 15$
K, meaning its bulk insolation is $135 \pm 30$ percent that of the Earth's.
Although the planet is likely too large to be rocky \citep{Rogers14}, 
its atmosphere is likely to be the focus of many future observations, providing
a cool analogue to the highly irradiated planets of a similar size found by 
\kep.

\subsection{EPIC 201465501?}
Is this a subsection? It's a star with a mass of ~0.2 Msun and a candidate with
a period of 18 days. I suppose it depends on the FPP.

@@

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems. 
One of these is EPIC 201367065, a three-planet system originally announced by
\citet{Crossfield15}. 
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed by
\kep \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of 
mini-Neptune sized planets.
Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.

We do not detect any significant transit timing variations

@@

\acknowledgements
We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for conversations and
suggestions which improved the quality of this manuscript.
